---
title       : Developing Data Products       
subtitle    : Diamond Price Prediction
author      : Karthikeyan Ramakrishnan
job         : DA
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overveiw 

1. This app shall be used for prediction of diamond
2. In General diamond price shall be measured by Carat size
3. As a first step we will build our linear model using dataset DIAMOND


--- .class #id 

## Model Preparation
First load our dataset diamond from UsingR package 
```{r,message=FALSE,out.height= 9}
library(UsingR);data(diamond)
```
Creating our linear model using lm function
```{r}
fit<-lm(price~carat,data=diamond)
coef(fit)
```
From the co efficient we estimate that 3721.0 dollar increase in price for every carat increase in mass of diamond


--- .class #id 

## Prediction

New data shall be loaded in variable name called new

```{r}

new = 3.75
predict(fit,newdata=data.frame(carat=new))

```

We predict that for 3.75 mass of diamond price for the same shall be 13694.22 dollar.

--- 

## Plot

Plotting the fitted regression line & data

```{r}
plot(diamond$carat,diamond$price,xlab="size of carat",ylab="Price",col="red")
        lines(diamond$carat,fit$fitted.values,col="blue")

```







